Peaks Over Threshold for Bursty Time Series

### 2018-06-28 article_springer/article_springer.Rmd
see, Pareto doesn't work either
points 1+2 addressed

  This article generalizes the Peaks Over Threshold (POT) model to the setting 
  where inter-event times are heavy-tailed. For high thresholds and 
  infinite-mean waiting times, we show that the times between threshold 
  crossings are Mittag-Leffler distributed, and thus form a "fractional 
  Poisson Process" which generalizes the standard Poisson Process.
  We provide graphical means of estimating model parameters and assessing 
  model fit. Along the way, we apply our inference method to a real-world
  bursty time series, and 
  show how the memory of the Mittag-Leffler distribution affects 
  the predictive distribution for the time until the next extreme event.

@@

flare_mags <- flares %>% ctre() %>% thin(k=500) %>% magnitudes()
flares_exponent <- flare_mags %>% qqestplot_static()

>>>>

  This article provides a new model for the threshold inter-exceedance _times_;
  the threshold exceedances are modeled via the standard 
  Peaks Over Threshold (POT) method.
  For high thresholds and 
  infinite-mean waiting times, we show that the times between threshold 
  crossings are Mittag-Leffler distributed, and thus form a "fractional 
  Poisson Process" which generalizes the standard Poisson Process of threshold
  exceedances.
  We provide graphical means of estimating model parameters and assessing 
  model fit. Along the way, we apply our inference method to a real-world
  bursty time series, and 
  show how the memory of the Mittag-Leffler distribution affects 
  the predictive distribution for the time until the next extreme event.

@@

flare_mags <- actuar::rpareto(n = 500, shape = 0.8, scale = 1)
flares_exponent <- flare_mags %>% qqestplot_static()
